Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-09 automatica/paper.tex
messing with benchmark section

Our benchmark suite consists of 26 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sampling times, 
leading to $191$ different benchmarks to evaluate the Multi-staged and Abstraction-based CEGIS algorithms.

%-------------------------------
\subsection{Description of the control benchmarks}
\label{exp:benchmarks}
%-------------------------------
\note{redo number and remove benchmarks that we can't solve}
The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
underactuated robot manipulator, 
%named acrobot, 
linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark (\#4) is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
benchmarks (\#5-8) correspond to high-order control system 
%discrete 
models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
The benchmarks \textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) deal with 
automotive cruise control models, where control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.

%There are two continuous stirred tank reactor models named 
\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a reaction~\cite{astrom2006advanced} in a 
%continuous flow stirred-
tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
dynamics of a 
%basic brushed 
direct-current electrical machine.

The \textit{Flexbeam} benchmark (\#14) is 
%a plant 
employed in vibration studies and models  
%the physical system consists of 
a flexible metallic structure with sensors and actuators. 
The \textit{guidance chen} benchmark (\#15) is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle. 
The \textit{helicopter} benchmark plant (\#16) describes the transitional and rotational dynamics 
%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
of a coaxial helicopter.

\textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18) 
are models for the cart position and the angle of an inverted pendulum placed on the cart,  
%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
which moves over a track through a DC motor.

The \textit{magpointer} (\#19) describes a magnetic pointer, 
% plant composed by a pointer employed in analogue gauges and indicators, 
whose angular position dynamics is controlled by a magnetic field. 
The \textit{magsuspension} describes (\#20) the dynamic of a magnetic car suspension system. 
The \textit{pendulum} (\#21) plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.

The \textit{Regulator} (\#22) consists of a linear model of a synchronous electrical machine% connected to an infinite bus
~\cite{KOKOTOVIC198023}. 
The \textit{springer-mass damper system} plant (\#23) is a standard model for the dynamics of several mechanical systems. 
%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark (\#24) describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.

The \textit{suspension} (\#25) models a single-wheel suspension system of a car, 
namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
The \textit{tapedriver} benchmark (\#26) models a computer tape driver, 
that is a computer storage device used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
3  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
4  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
5  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
8 & Cstr & 3 & & ~\xmark & & ~\xmark \\
9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

Our benchmark suite consists of 20 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time.

%-------------------------------
\subsection{Description of the control benchmarks}
\label{exp:benchmarks}
%-------------------------------

The \textit{acrobot}plant corresponds to the model of a two-link 
underactuated robot manipulator, 
%named acrobot, 
linearized by partial feedback linearization~\cite{acrobot}.
%The \textit{antenna} benchmark (\#2) 
%describes the dynamics of the azimuth angle of an antenna 
%motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev}  plant corresponds to the model of a simple 
eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
The \textit{bioreactor} benchmark  is a linear model 
%identified by least squares 
of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.

The \textit{Chen\_ex1} and \textit{Chen\_ex2}
benchmarks correspond to high-order control system 
%discrete 
models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with 
automotive cruise control models, where control is used to keep 
constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.

%There are two continuous stirred tank reactor models named 
\textit{cstr}  and \textit{cstrtmp}  describe the PH dynamics of a reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a reaction~\cite{astrom2006advanced} in a 
%continuous flow stirred-
tank reactor. The \textit{DC motor} plant  describes the velocity 
dynamics of a 
%basic brushed 
direct-current electrical machine.

The \textit{Flexbeam} benchmark  is 
%a plant 
employed in vibration studies and models  
%the physical system consists of 
a flexible metallic structure with sensors and actuators. 
The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle. 
The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
of a coaxial helicopter.

%\textit{Invpendulum\_cartpos}  and 
The \textit{Invpendulum\_pendang}  
describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
which moves over a track through a DC motor.

The \textit{magpointer}  describes a magnetic pointer, 
% plant composed by a pointer employed in analogue gauges and indicators, 
whose angular position dynamics is controlled by a magnetic field. 
The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.

The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
~\cite{KOKOTOVIC198023}. 
The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.

The \textit{suspension} models a single-wheel suspension system of a car, 
namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
The \textit{tapedriver} benchmark  models a computer tape driver, 
that is a computer storage device used to read and write data on magnetic tapes.

@@

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
